Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-01-11 PAPER.tex
removed text about negative P_ins

In our code, we simulate $20$ realizations of $P_{in}$ by bootstrapping over baselines, as explained in Section \ref{sec:Boot}, yielding $P_{\rm in}$ values that range from $\sim$$-10^{13}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$ (negative $P_{\rm in}$ is injected when one copy of \textbf{e} in Equation \eqref{eq:Pin} is negative and the other is positive) to $\sim$10$^{13}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$. We also run $40$ total EoR injection levels, resulting in a total of $800$ data points on our $P_{\rm in}$ vs. $P_{\rm out}$ grid. 
%Additionally, we have verified that the transfer function is symmetric for negative and positive $P_{\rm in}$'s, and so we fold all the values into positive ones to increase our signal-to-noise.

>>>>

In our code, we simulate $20$ realizations of $P_{in}$ by bootstrapping over baselines, as explained in Section \ref{sec:Boot}, yielding $P_{\rm in}$ values that range from $\sim$$10^{2}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$ to $\sim$10$^{16}$ mK$^{2}$ (h$^{-1}$ Mpc)$^{3}$. We also run $25$ total EoR injection levels, resulting in a total of $500$ data points on our $P_{\rm in}$ vs. $P_{\rm out}$ grid. 
%Additionally, we have verified that the transfer function is symmetric for negative and positive $P_{\rm in}$'s, and so we fold all the values into positive ones to increase our signal-to-noise.
